Automatic discovery of cell types and microcircuitry from neural connectomics

### 2014-01-07 docs/paper.tex
updated paper text

\title{Automatic discovery of circuit structure from neural connectomics}
\author{Eric Jonas$^1$, Konrad Kording$^{2, 3,4}$}

@@

% \begin{addendum}
%  \item Put acknowledgements here.
%  \item[Competing Interests] The authors declare that they have no
% competing financial interests.
%  \item[Correspondence] Correspondence and requests for materials
% should be addressed to A.B.C.~(email: myaddress@nowhere.edu).
% \end{addendum}
\newpage
\section{Supplemental}

@@

\href{http://spatialrelation.github.io }{http://spatialrelation.github.io}

>>>>

\title{Automatic discovery of cell types and microcircuitry from neural connectomics}
\author{Eric Jonas$^1$, Konrad Kording$^{2, 3,4}$}

@@

% \begin{addendum}
%  \item Put acknowledgements here.
%  \item[Competing Interests] The authors declare that they have no
% competing financial interests.
%  \item[Correspondence] Correspondence and requests for materials
% should be addressed to A.B.C.~(email: myaddress@nowhere.edu).
% \end{addendum}
\newpage
\section{Supplemental Material}

@@

\href{http://https://github.com/ericmjonas/netmotifs}{https://github.com/ericmjonas/netmotifs/}

Please contact the author for pre-publication access.
